Higher-Order unification for free!

### 2024-04-11 paper/main.tex
small update

\section{Handling of \notllambda}\label{sec:beta}
\noteD[inline]{Dire che OL fallisce tutte le unif not in llambda, e poi modificare 
le progress e la decomp}

@@

\paragraph{Decompilation}
We suppose that the unification of the object language rejects any unification
between two terms where at least one of them is not in \llambda 
(this includes unifications like $X = Y\appsep Z$ and $X\appsep Y = X \appsep Y$).
Therefore, a failure is thrown if any \linkbeta remains in \linkStore at the
begin of decompilation, i.e. all \linkbeta should be solved before decompilation.

@@

\begin{definition}[\progBetaFail]
  If it exists a link $l' \in \linkStore$ with same \lhs as $l$, or the \lhs 
  of $l$ become rigid, then unification fail.
  \footnote{This is a consequence of what claimed in \linkbeta decompilation}
  \label{def:progBetaFail}
\end{definition}

>>>>

\section{Handling of \notllambda}\label{sec:beta}

In this section we suppose the unification of the object language between two
terms $t_1$ and $t_2$ to fail each time at least one of the between $t_1$ or
$t_2$ is outside $\llambda$. This means for instance that $X \nUo Y \appsep Z$ and 
$X\appsep Y \nUo X\appsep Y$.

@@

\paragraph{Decompilation}
A failure is thrown if any \linkbeta remains in \linkStore at the
begin of decompilation, i.e. all \linkbeta should be solved before decompilation.

@@

\begin{definition}[\progBetaFail]
  If it exists a link $l' \in \linkStore$ with same \lhs as $l$, or the \lhs 
  of $l$ become rigid, then unification fail.
  \label{def:progBetaFail}
\end{definition}
